\chapter{Project Statement}
\thispagestyle{plain} 


\section{Problem Statement} 
To implement stateful bolts in Storm. Using Storm which is a fault-tolerant real-time distributed system and making bolts stateful which will make Storm process real-time data more efficiently by reducing redundant computation.

\section{Technology Used}
\subsection{Apache ZooKeeper}
ZooKeeper is a centralized service for maintaining configuration information, naming, providing distributed synchronization, and providing group services. All of these kinds of services are used in some form or another by distributed applications. Each time they are implemented there is a lot of work that goes into fixing the bugs and race conditions that are inevitable. Because of the difficulty of implementing these kinds of services, applications initially usually skimp on them ,which make them brittle in the presence of change and difficult to manage. Even when done correctly, different implementations of these services lead to management complexity when the applications are deployed.
\subsection{Java}
It is general-purpose,concurrent,class-based,object-oriented computer programming language that is specifically designed to have as few implementation dependencies as possible. It is intended to let application developers "write once, run anywhere" (WORA), meaning that code that runs on one platform does not need to be recompiled to run on another.Java applications are typically compiled to bytecode(class file) that can run on any Java virtual machine (JVM) regardless of computer architecture. Java is, as of 2012, one of the most popular programming languages in use, particularly for client-server web applications, with a reported 9 million developers.Java was originally developed by James Gosling at Sun Microsystems (which has since merged into Oracle Corporation) and released in 1995 as a core component of Sun Microsystems' Java platform. The language derives much of its syntax from C and C++, but it has fewer low-level facilities than either of them.
\subsection{Clojure}
{\bfseries Clojure} is a dialect of the Lisp programming language created by Rich Hickey. It is a functional general-purpose language. Its focus on programming with immutable values and explicit progression-of-time constructs are intended to facilitate the development of more robust programs, particularly multithreaded ones.
Clojure runs on the Java Virtual Machine, Common Language Runtime, and JavaScript engines. Like other Lisps, Clojure treats code as data and has a sophisticated macro system.  

